---
title: "Pre-Test: Dilution in Abstract Causal Chains (8 Links)"
author: "Simon Stephan"
date: "11-03-2021"
output: html_document
---

```{r setup, include=FALSE}
# packages
library(ez)
library(reshape2)
library(reshape)
library(ggplot2)
library(plyr)
library(pastecs)
library(ez)
library(data.table)
library(tidyverse) 

library(showtext)


font_add_google("Poppins", "Poppins")
font_add_google("Roboto Mono", "Roboto Mono")
showtext_auto()
```


```{r}
# Read in data
#tdata.wide <- read.delim("dummy_data.txt", header=TRUE, sep="\t", na.strings="NA", dec=".", strip.white=TRUE)
tdata <- read.delim("Data_abstract_chains_pretest.txt", header=TRUE, sep="\t", na.strings="NA", dec=".", strip.white=TRUE)
```

# Results 

## Demographics

```{r}
# demographics 
tdata_age <- tdata
min(tdata_age$Age)
max(tdata_age$Age)
mean(tdata_age$Age)
sd(tdata_age$Age)
```
Min = 18 years, 
Max = 64 years, 
Mean = 31.48 years, 
SD = 11.67 years



```{r}
# 1 = male, 2 = female, 3 = other
table(tdata$Sex)
```


1 = Male, 2 = Female, 3 = Non-binary



```{r, echo = FALSE}
# to create a bar char, the data must be in long format and only contain the relevant dependent variables

# 1. make a subset with only the relevant dvs 

tdata_sub <- subset(tdata, select = 1:10)

tdata_8links <- subset(tdata, Links == "eight") # thats the only condition but we use a generic code here 
tdata_8links <- subset(tdata_8links, select = c(1:10))



# 2. reshape into long format 

tdata_8links <- tdata_8links %>% gather(variable, value, 3:10)

tdata_8links$variable <- factor(tdata_8links$variable, levels = c("strength_1", "strength_2", "strength_3", "strength_4", 
                                                                  "strength_5", "strength_6", "strength_7", "strength_8"), 
                          labels = c("1st", "2nd", "3rd", "4th", "5th", "6th", "7th", "8th"))


tdata_8links$value <- tdata_8links$value * 0.01


```

# Graphs


```{r}
myTheme <- theme(plot.title = element_text(face="bold", size = 22),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 18, angle = 0), 
        axis.text.y = element_text(size = 14, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))


library(see)

tdata_sub <- tdata_8links

## first, turn sID into a factor
tdata_sub$sID <- factor(tdata_sub$sID)

pd <- position_dodge(width = 0.3)

tdata_sub$valueJitter <- jitter(tdata_sub$value, factor = 1, amount = 0.04)

theme_set(theme_light(base_size = 20, base_family = "Poppins"))

# new labes for the facets 
#process.labs <- c("Process: Generative", "Process: Preventive")
#names(process.labs) <- c("generative", "preventive")

#valence.labs <- c("Effect valence: Positive", "Effect Valence: Negative")
#names(valence.labs) <- c("positive", "negative")


g <- ggplot(tdata_sub, aes(x=variable, y=valueJitter, group = sID)) +
  guides(fill=FALSE)+
  #facet_grid(Valence ~ Process, labeller = labeller(Process = process.labs, Valence = valence.labs))+
  #ggtitle("Subjects' causal srength ratings") +
  scale_y_continuous(limits = c(-0.05, 1.05), breaks=seq(0, 1, 0.1), expand = c(0,0)) +
  #scale_x_discrete(labels=c("Downward chain", "Upward chain")) +
  #stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black", alpha =0.5) +
  geom_violinhalf(aes(y = value, group = variable), color = NA, position=position_dodge(1), alpha = 0.2)+
  geom_line(position = pd, color = "red", size = 1, alpha=0.04) +
  geom_point(position = pd, alpha = 0.2, fill = "red", color = "red") +
  stat_summary(aes(y = value,group=1), fun.data = mean_cl_boot, geom = "errorbar", width = 0, size = 1) +
  stat_summary(aes(y = value,group=1), fun.y=mean, colour="red", geom="line",group=1, size = 1.5, linetype = "solid", alpha = 0.6)+
  stat_summary(aes(y = value,group=1), fun.y=mean, geom="point", color = "black", fill = "red", shape = 22, size = 5, group=1, alpha = 0.8)+
  stat_summary(aes(y = value,group=1), fun.y=median, geom="point", color = "black", shape = 8, size = 5, group=1, alpha = 1, position = position_dodge(width = 0.5))+
  labs(x = "Link of the Chain", y = "Causal Strength Rating") +
  #scale_color_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  #scale_fill_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  theme(legend.position = "none")+
  myTheme
g


#ggsave("results_lines8.svg",width=6,height=6)
#ggsave("results_lines8.pdf",width=6,height=6)
```




# Descriptive Stats

```{r, echo = FALSE, warning = FALSE, message = FALSE}

################################################################################################################
##################################### Statistical Analyses #####################################################
################################################################################################################
library(pastecs)
library(lme4)
library(nlme)
library(ez)


##################################### Create descriptive stats ###################################

by(tdata_sub$value, list(tdata_sub$variable), stat.desc , basic = FALSE)

##################################### Model ######################################################
```

# Inferential Statistics

Within-ANOVA to test the effect of Link:

```{r}
library(afex)
library(emmeans)
tdata_sub <- tdata_8links
a1 <- aov_car(value ~ variable + Error(sID/(variable)), tdata_sub)
a1


```
Is significant. 



What our theory of causal strength dilution predicts is a specific negative linear trend; so we test this

```{r}
# Polynomial Contrasts
#library(Rcmdr)
# Quantitative Trend analysis

contrasts(tdata_sub$variable) <- "contr.poly" # define contrast coefficients

Trend <- aov(value ~ variable, data=tdata_sub)
summary.lm(Trend)


```
The only significant polynomial trend is a negative linear trend (see "variable.L"). 



Again some descriptive Stats in a more compact format:

```{r}
# for 8 links 

tdata_sub <- tdata_8links

# same ANOVA as before
lmeModel <- lmer(value ~ variable + (1|sID), data=tdata_sub)

# follow-up analysis 

ls1 <- lsmeans(a1, c("variable")) # joint evaluation (basically gives the same table)
ls1
```

Now we analyse the contrast between the strength ratings for the 1st and the 8th Link of the chain, as this is our measure of strength dilution:

```{r}
# contrast 1st vs. 8th link 

tdata_18 <- subset(tdata_8links, variable == "1st" | variable == "8th")
tdata_sub <- tdata_18

a1 <- aov_car(value ~ variable + Error(sID/(variable)), tdata_sub)

############### 
# a conditional analysis 

ls2 <- lsmeans(a1, c("variable")) # group means by between-condition
ls2

# simple main effects 
pairs(ls2) # compares rep-measure differences separately for each between-factor level

```
This difference is significant (see "contrast").

What is the effect size (d)?

```{r}
# compute Cohen's d
library(effsize)
library(rstatix)

tdata_18$variable <- factor(tdata_18$variable, levels = c("1st", "8th"))

tdata_18 %>% cohens_d(value ~ variable, paired = T)

```


Get SE for d

```{r}

d <- 0.2649241	

dat_1st <- subset(tdata_18, variable == "1st")
dat_8th <- subset(tdata_18, variable == "8th")

cor.test(dat_1st$value, dat_8th$value)

cor <- 0.03321437 
n <- 100

SEd <- sqrt((1/n + d^2/n)*2*(1-cor))
SEd
```