---
title: "The dilution of causal strength in abstract chains"
author: "Simon Stephan"
output: html_document
---

```{r setup, include=FALSE}
# packages
library(ez)
library(reshape2)
library(reshape)
library(ggplot2)
library(plyr)
library(pastecs)
library(ez)
library(data.table)
library(tidyverse) 

library(showtext)


font_add_google("Poppins", "Poppins")
font_add_google("Roboto Mono", "Roboto Mono")
showtext_auto()
```


```{r}
#tdata.wide <- read.delim("dummy_data.txt", header=TRUE, sep="\t", na.strings="NA", dec=".", strip.white=TRUE)
tdata <- read.delim("Data_Exp_Abstract_Chains.txt", header=TRUE, sep="\t", na.strings="NA", dec=".", strip.white=TRUE)
```




# Results 

## Demographics

```{r}
# demographics 

tdata_age <- tdata 

min(tdata_age$Age)
max(tdata_age$Age)
mean(tdata_age$Age)
sd(tdata_age$Age)

# 1 = male, 2 = female, 3 = other
table(tdata$Sex)
```
1 = male, 2 = female




```{r, echo = FALSE}
# reorder factor 

#tdata <- subset(tdata, Last_Node_Answer == "correct")

tdata$Order <- factor(tdata$Order, levels = c("four_eight", "eight_four")) # Order in which chains were shown to subjects

# to create a bar char, the data must be in long format and only contain the relevant dependent variables

# 1. make a subset with only the relevant dvs 

tdata_sub <- subset(tdata, select = 1:14)


tdata_4links <- subset(tdata_sub, select = c(1,2,3,5,7,9))
tdata_8links <- subset(tdata_sub, select = c(1,2,4,6,8,10:14))



# 2. reshape into long format 
tdata_4links <- tdata_4links %>% gather(variable, value, 3:6)
tdata_8links <- tdata_8links %>% gather(variable, value, 3:10)

tdata_4links$variable <- factor(tdata_4links$variable, levels = c("strength_1_4", "strength_2_4", "strength_3_4",
                                                                  "strength_4_4"), 
                          labels = c("1st", "2nd", "3rd", "4th"))

tdata_8links$variable <- factor(tdata_8links$variable, levels = c("strength_1_8", "strength_2_8", "strength_3_8",
                                                                  "strength_4_8", "strength_5_8", "strength_6_8",
                                                                  "strength_7_8", "strength_8_8"), 
                          labels = c("1st", "2nd", "3rd", "4th", "5th", "6th", "7th", "8th"))


tdata_4links$value <- tdata_4links$value * 0.01 # Recode DV so that values range from 0 to 1
tdata_8links$value <- tdata_8links$value * 0.01


```

# Graphs

For the 4-links chain condition

```{r}
myTheme <- theme(plot.title = element_text(face="bold", size = 22),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 18, angle = 0), 
        axis.text.y = element_text(size = 14, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))


library(see)

tdata_sub <- tdata_4links

## first, turn sID into a factor
tdata_sub$sID <- factor(tdata_sub$sID)

pd <- position_dodge(width = 0.3)

tdata_sub$valueJitter <- jitter(tdata_sub$value, factor = 1, amount = 0.04)

theme_set(theme_light(base_size = 20, base_family = "Poppins"))

# new labes for the facets 
#process.labs <- c("Process: Generative", "Process: Preventive")
#names(process.labs) <- c("generative", "preventive")

#valence.labs <- c("Effect valence: Positive", "Effect Valence: Negative")
#names(valence.labs) <- c("positive", "negative")


g <- ggplot(tdata_sub, aes(x=variable, y=valueJitter, group = sID)) +
  guides(fill=FALSE)+
  #facet_grid(Valence ~ Process, labeller = labeller(Process = process.labs, Valence = valence.labs))+
  #ggtitle("Subjects' causal srength ratings") +
  scale_y_continuous(limits = c(-0.05, 1.05), breaks=seq(0, 1, 0.1), expand = c(0,0)) +
  #scale_x_discrete(labels=c("Downward chain", "Upward chain")) +
  #stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black", alpha =0.5) +
  geom_violinhalf(aes(y = value, group = variable), color = NA, position=position_dodge(1), alpha = 0.2)+
  geom_line(position = pd, color = "red", size = 1, alpha=0.04) +
  geom_point(position = pd, alpha = 0.2, fill = "red", color = "red") +
  stat_summary(aes(y = value,group=1), fun.data = mean_cl_boot, geom = "errorbar", width = 0, size = 1) +
  stat_summary(aes(y = value,group=1), fun.y=mean, colour="red", geom="line",group=1, size = 1.5, linetype = "solid", alpha = 0.6)+
  stat_summary(aes(y = value,group=1), fun.y=mean, geom="point", color = "black", fill = "red", shape = 22, size = 5, group=1, alpha = 0.8)+
  stat_summary(aes(y = value,group=1), fun.y=median, geom="point", color = "black", shape = 3, size = 4, group=1, alpha = 1, position = position_dodge(width = 0.5))+
  labs(x = "Link of Chain", y = "Causal Strength Rating") +
  #scale_color_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  #scale_fill_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  theme(legend.position = "none")+
  myTheme
g


#ggsave("results_lines4.svg",width=7,height=6)
#ggsave("results_lines4.pdf",width=7,height=6)
```

For the 8-links chain condition

```{r}
myTheme <- theme(plot.title = element_text(face="bold", size = 22),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 18, angle = 0), 
        axis.text.y = element_text(size = 14, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))


library(see)

tdata_sub <- tdata_8links

## first, turn sID into a factor
tdata_sub$sID <- factor(tdata_sub$sID)

pd <- position_dodge(width = 0.3)

tdata_sub$valueJitter <- jitter(tdata_sub$value, factor = 1, amount = 0.04)

theme_set(theme_light(base_size = 20, base_family = "Poppins"))

# new labes for the facets 
#process.labs <- c("Process: Generative", "Process: Preventive")
#names(process.labs) <- c("generative", "preventive")

#valence.labs <- c("Effect valence: Positive", "Effect Valence: Negative")
#names(valence.labs) <- c("positive", "negative")


g <- ggplot(tdata_sub, aes(x=variable, y=valueJitter, group = sID)) +
  guides(fill=FALSE)+
  #facet_grid(Valence ~ Process, labeller = labeller(Process = process.labs, Valence = valence.labs))+
  #ggtitle("Subjects' causal srength ratings") +
  scale_y_continuous(limits = c(-0.05, 1.05), breaks=seq(0, 1, 0.1), expand = c(0,0)) +
  #scale_x_discrete(labels=c("Downward chain", "Upward chain")) +
  #stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black", alpha =0.5) +
  geom_violinhalf(aes(y = value, group = variable), color = NA, position=position_dodge(1), alpha = 0.2)+
  geom_line(position = pd, color = "red", size = 1, alpha=0.04) +
  geom_point(position = pd, alpha = 0.2, fill = "red", color = "red") +
  stat_summary(aes(y = value,group=1), fun.data = mean_cl_boot, geom = "errorbar", width = 0, size = 1) +
  stat_summary(aes(y = value,group=1), fun.y=mean, colour="red", geom="line",group=1, size = 1.5, linetype = "solid", alpha = 0.6)+
  stat_summary(aes(y = value,group=1), fun.y=mean, geom="point", color = "black", fill = "red", shape = 22, size = 5, group=1, alpha = 0.8)+
  stat_summary(aes(y = value,group=1), fun.y=median, geom="point", color = "black", shape = 3, size = 4, group=1, alpha = 1, position = position_dodge(width = 0.5))+
  labs(x = "Link of Chain", y = "Causal Strength Rating") +
  #scale_color_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  #scale_fill_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  theme(legend.position = "none")+
  myTheme
g


#ggsave("results_lines8.svg",width=7,height=6)
#ggsave("results_lines8.pdf",width=7,height=6)
```




# Descriptive Stats

8-links chain condition:

```{r, echo = FALSE, warning = FALSE, message = FALSE}

################################################################################################################
##################################### Statistical Analyses #####################################################
################################################################################################################
library(pastecs)
library(lme4)
library(nlme)
library(ez)


##################################### Create descriptive stats ###################################

by(tdata_sub$value, list(tdata_sub$variable), stat.desc , basic = FALSE)



##################################### Model ######################################################
```
4-links chain condition: 

```{r}
tdata_sub <- tdata_4links

by(tdata_sub$value, list(tdata_sub$variable), stat.desc , basic = FALSE)



```


# Inferential Statistics

8-links chain:

Repeated-Measures ANOVA 

```{r}


library(afex)
library(emmeans)
tdata_sub <- tdata_8links
a1 <- aov_car(value ~ variable + Error(sID/(variable)), tdata_sub)
a1


```
Main effect of link of chain ("variable").


Is there a negative linear trend? Conduct a polynomial contrast analysis:


```{r}
# Polynomial Contrasts
#library(Rcmdr)
# Quantitative Trend analysis

contrasts(tdata_sub$variable) <- "contr.poly" # define contrast coefficients

Trend <- aov(value ~ variable, data=tdata_sub)
summary.lm(Trend)

```
Yes, the only sign. quantitative trend is a negative linear trend (see "variable.L"). 


Now for the 4-links chain: 

Repeated-Measures ANOVA: 

```{r}
# now the same analysis for the condition with 4 links 

library(afex)
library(emmeans)
tdata_sub <- tdata_4links
a2 <- aov_car(value ~ variable + Error(sID/(variable)), tdata_sub)
a2


```

Main effect of Link of chain. 

Negative Trend? 

```{r}
# Polynomial Contrasts
#library(Rcmdr)
# Quantitative Trend analysis

contrasts(tdata_sub$variable) <- "contr.poly" # define contrast coefficients

Trend <- aov(value ~ variable, data=tdata_sub)
summary.lm(Trend)

```
Yes. 


A more compact list of the means: 

8-links chain

```{r}
# for 8 links 

tdata_sub <- tdata_8links

# same ANOVA as before
lmeModel <- lmer(value ~ variable + (1|sID), data=tdata_sub)

# follow-up analysis 

ls1 <- lsmeans(a1, c("variable")) # joint evaluation (basically gives the same table)
ls1
```

Our measure for dilution: Difference between first and last link. 

8-links chain contrast:

```{r}
# contrast 1st vs. 8th link 

tdata_18 <- subset(tdata_8links, variable == "1st" | variable == "8th")
tdata_sub <- tdata_18

a1 <- aov_car(value ~ variable + Error(sID/(variable)), tdata_sub)

# contrast

ls2 <- lsmeans(a1, c("variable")) # group means by between-condition
ls2

# simple main effects 
t <- pairs(ls2) # compares rep-measure differences separately for each between-factor level
t

```

Yes, the contrast is significant (see "contrast" output). 




Compute a 95 CI for the difference:


```{r}
confint(t, adjust = "none")
```
Manually:

```{r}

t <- qt(0.975, 99, lower.tail = TRUE, log.p = FALSE) # get the correct t-Value


effect <- "Mdiff"
Mdiff <- 0.129  # the estimated difference from the output above
SE <- 0.0323  # its SE 
CI <- SE*t
CI_low <- Mdiff - CI
CI_up <- Mdiff + CI

Mdiff
CI_low
CI_up



# Plot 

myTheme <- theme(plot.title = element_text(face="bold", size = 22),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 18, angle = 0), 
        axis.text.y = element_text(size = 25, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        #panel.grid.minor = element_blank(), 
        #panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))

theme_set(theme_light(base_size = 30, base_family = "Poppins"))



barchart <- ggplot()+
  myTheme+
  #guides(fill=FALSE)+
  #facet_wrap(~Latency + SampleSize, ncol=2)+
  #ggtitle("Mean difference (95% CI)") +
  #coord_cartesian(ylim=c(-0.1,2)) + 
  scale_y_continuous(limits = c(-0.1, 0.5), breaks=seq(-0.1, 0.5, 0.1), expand = c(0,0)) +
  scale_x_discrete(labels=c("r")) +
  #annotate("rect", xmin=1.7, xmax=2.3, ymin=0.95, ymax=1.05, color="#31a354", fill = "white", size = 1) +
  #stat_summary(fun.y=mean, colour="grey20", geom="point", shape = 21, size = 3)+
  #stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black")+
  #stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.90), width = 0.2) +
  #geom_jitter(width = 0.3, height = 0.02, alpha = 0.6, colour = "red") +
  #ggtitle("Means (95% bootstr. CIs)") +
  #theme(axis.text.x = element_text(size = 10, angle = 0, hjust = 0.5))+
  labs(x= "", y = "1st - 8th Link") +
  #scale_color_manual(values=c("#005083",  "#f0b64d"))# +
  #scale_fill_manual(values=c("#969696",  "#969696"))
  #annotate("point", x = 1, y = 100, colour = "firebrick", size = 2)+
  #annotate(xmin = -Inf, xmax = Inf, ymin = 4.77-1.96*0.297, ymax = 4.77+1.96*0.297, geom = "rect", alpha = 0.2, fill = "firebrick")+
  #annotate(xmin = -Inf, xmax = Inf, ymin = 5.02-1.96*0.372, ymax = 5.02+1.96*0.372, geom = "rect", alpha = 0.2, fill = "blue")+
  #annotate(geom = "hline",yintercept = 100, y = 100, color = "red")+
  annotate("pointrange", x = 1, y = Mdiff, ymin = CI_low, ymax = CI_up, colour = "black", size = 1.5, shape = 24, fill = "darkgrey")+
  #annotate("pointrange", x = 2, y = 5.02, ymin = 5.02-1.96*0.372, ymax = 5.02+1.96*0.372, colour = "blue", size = 0.8, shape = 15)+
  #annotate("text", x = 0.5, y = 2.6, family = "Poppins", size = 6, color = "gray20", label = "Impfeffekt")+
  #geom_curve(aes(x = 0.5, y = 3, xend = 0.9, yend = 4),arrow = arrow(length = unit(0.03, "npc")),color = "gray20", curvature = +0.2)+
  #annotate("text", x = 1.8, y = 2.6, family = "Poppins", size = 6, color = "gray20", label = "Dosierungseffekt")+
  #geom_curve(aes(x = 1.8, y = 3, xend = 2, yend = 4),arrow = arrow(length = unit(0.03, "npc")),color = "gray20", curvature = +0.2)+
  annotate(geom = "hline",yintercept = 0, y = 0, color = "red", size = 1.2)+
  theme(plot.background = element_rect(
    fill = "white",
    colour = "black",
    size = 1
  ),
    axis.title.y = element_text(size = 30))


barchart

#ggsave("delta_1st_vs_8th.svg",width=2.5,height=4)
ggsave("delta_1st_vs_8th.pdf",width=2.5,height=4)



```


What Cohen's d does this difference correspond to? 

```{r}

tdata_18$variable <- factor(tdata_18$variable, levels = c("1st", "8th"))



library(rstatix)

tdata_18 %>% cohens_d(value ~ variable, 
                      paired = T, 
                      ci = TRUE, 
                      conf.level = 0.95,
                      ci.type = "perc",
                      nboot = 1000)

```



Get SE for d

```{r}
# based on the estimated CI 
half_CI_width <- (0.58 - 0.22)*0.5
SE_d <- half_CI_width/1.96
SE_d
```




Now the same for the 4-links chain:


```{r}
library(afex)
library(emmeans)
tdata_sub <- tdata_4links
a2 <- aov_car(value ~ variable + Error(sID/(variable)), tdata_sub)


tdata_sub <- tdata_4links

# same ANOVA as before
lmeModel <- lmer(value ~ variable + (1|sID), data=tdata_sub)


ls1 <- lsmeans(a2, c("variable")) # joint evaluation (basically gives the same table)
ls1
```
Contrast for first vs. last link:

```{r}
# contrast 1st vs. 8th link 

tdata_14 <- subset(tdata_4links, variable == "1st" | variable == "4th")
tdata_sub <- tdata_14

a1 <- aov_car(value ~ variable + Error(sID/(variable)), tdata_sub)


ls2 <- lsmeans(a1, c("variable")) # group means by between-condition
ls2

# simple main effects 
t <- pairs(ls2) # compares rep-measure differences separately for each between-factor level
t
```
also significant. 


```{r}
confint(t, adjust = "none")
```


Confidence intervall for the difference:

```{r}

t <- qt(0.975, 99, lower.tail = TRUE, log.p = FALSE)
#t

effect <- "Mdiff"
Mdiff <- 0.0884 
SE <- 0.0212
CI <- SE*t
CI_low <- Mdiff - CI
CI_up <- Mdiff + CI

Mdiff
CI_low
CI_up



# Plot 

myTheme <- theme(plot.title = element_text(face="bold", size = 22),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 18, angle = 0), 
        axis.text.y = element_text(size = 25, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        #panel.grid.minor = element_blank(), 
        #panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))

theme_set(theme_light(base_size = 30, base_family = "Poppins"))



barchart <- ggplot()+
  myTheme+
  #guides(fill=FALSE)+
  #facet_wrap(~Latency + SampleSize, ncol=2)+
  #ggtitle("Mean difference (95% CI)") +
  #coord_cartesian(ylim=c(-0.1,2)) + 
  scale_y_continuous(limits = c(-0.1, 0.5), breaks=seq(-0.1, 0.5, 0.1), expand = c(0,0)) +
  scale_x_discrete(labels=c("r")) +
  #annotate("rect", xmin=1.7, xmax=2.3, ymin=0.95, ymax=1.05, color="#31a354", fill = "white", size = 1) +
  #stat_summary(fun.y=mean, colour="grey20", geom="point", shape = 21, size = 3)+
  #stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black")+
  #stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.90), width = 0.2) +
  #geom_jitter(width = 0.3, height = 0.02, alpha = 0.6, colour = "red") +
  #ggtitle("Means (95% bootstr. CIs)") +
  #theme(axis.text.x = element_text(size = 10, angle = 0, hjust = 0.5))+
  labs(x= "", y = "1st - 4th Link") +
  #scale_color_manual(values=c("#005083",  "#f0b64d"))# +
  #scale_fill_manual(values=c("#969696",  "#969696"))
  #annotate("point", x = 1, y = 100, colour = "firebrick", size = 2)+
  #annotate(xmin = -Inf, xmax = Inf, ymin = 4.77-1.96*0.297, ymax = 4.77+1.96*0.297, geom = "rect", alpha = 0.2, fill = "firebrick")+
  #annotate(xmin = -Inf, xmax = Inf, ymin = 5.02-1.96*0.372, ymax = 5.02+1.96*0.372, geom = "rect", alpha = 0.2, fill = "blue")+
  #annotate(geom = "hline",yintercept = 100, y = 100, color = "red")+
  annotate("pointrange", x = 1, y = Mdiff, ymin = CI_low, ymax = CI_up, colour = "black", size = 1.5, shape = 24, fill = "darkgrey")+
  #annotate("pointrange", x = 2, y = 5.02, ymin = 5.02-1.96*0.372, ymax = 5.02+1.96*0.372, colour = "blue", size = 0.8, shape = 15)+
  #annotate("text", x = 0.5, y = 2.6, family = "Poppins", size = 6, color = "gray20", label = "Impfeffekt")+
  #geom_curve(aes(x = 0.5, y = 3, xend = 0.9, yend = 4),arrow = arrow(length = unit(0.03, "npc")),color = "gray20", curvature = +0.2)+
  #annotate("text", x = 1.8, y = 2.6, family = "Poppins", size = 6, color = "gray20", label = "Dosierungseffekt")+
  #geom_curve(aes(x = 1.8, y = 3, xend = 2, yend = 4),arrow = arrow(length = unit(0.03, "npc")),color = "gray20", curvature = +0.2)+
  annotate(geom = "hline",yintercept = 0, y = 0, color = "red", size = 1.2)+
  theme(plot.background = element_rect(
    fill = "white",
    colour = "black",
    size = 1
  ), 
    axis.title.y = element_text(size = 30))


barchart

#ggsave("delta_1st_vs_4th.svg",width=2.5,height=4)
ggsave("delta_1st_vs_4th.pdf",width=2.5,height=4)



```


What Cohen's d does this correspond to? 

```{r}

tdata_14$variable <- factor(tdata_14$variable, levels = c("1st", "4th"))


library(rstatix)
tdata_14 %>% cohens_d(value ~ variable, 
                      paired = T,
                      ci = TRUE, 
                      conf.level = 0.95,
                      ci.type = "perc",
                      nboot = 1000)

```

Get SE for d

```{r}
# based on the estimated CI 
half_CI_width <- (0.57-0.26)*0.5
SE_d <- half_CI_width/1.96
SE_d
```







# Interaction 

This is exploratory


```{r, echo = FALSE}
# reorder factor 

#tdata <- subset(tdata, Last_Node_Answer == "correct")

tdata$Order <- factor(tdata$Order, levels = c("four_eight", "eight_four"))

# to create a bar char, the data must be in long format and only contain the relevant dependent variables

# 1. make a subset with only the relevant dvs 

tdata_sub <- subset(tdata, select = 1:14)


tdata_4links <- subset(tdata_sub, select = c(1,2,3,5,7,9))
tdata_8links <- subset(tdata_sub, select = c(1,2,4,6,8,10:14))



# 2. reshape into long format 
tdata_4links <- tdata_4links %>% gather(variable, value, 3:6)
tdata_8links <- tdata_8links %>% gather(variable, value, 3:10)

tdata_4links$variable <- factor(tdata_4links$variable, levels = c("strength_1_4", "strength_2_4", "strength_3_4",
                                                                  "strength_4_4"))

tdata_8links$variable <- factor(tdata_8links$variable, levels = c("strength_1_8", "strength_2_8", "strength_3_8",
                                                                  "strength_4_8", "strength_5_8", "strength_6_8",
                                                                  "strength_7_8", "strength_8_8"))


tdata_4links$value <- tdata_4links$value * 0.01
tdata_8links$value <- tdata_8links$value * 0.01


tdata_all <- rbind(tdata_4links, tdata_8links)

tdata_1814 <- subset(tdata_all, variable == "strength_1_4" | variable == "strength_4_4" | variable == "strength_1_8" | 
                       variable == "strength_8_8")

tdata_1814$variable <- factor(tdata_1814$variable, levels=c("strength_1_4", "strength_4_4", "strength_1_8", "strength_8_8"))

tdata_1814$Links <- c(rep("four", 200),rep("eight", 200))

tdata_1814$variable2 <- c(rep("first", 100), rep("last", 100), rep("first", 100), rep("last", 100))

tdata_1814$Links <- factor(tdata_1814$Links, levels=c("four", "eight"))

tdata_1814$variable2 <- factor(tdata_1814$variable2, levels=c("first", "last"))

```


# Graph of interaction 



```{r}
myTheme <- theme(plot.title = element_text(face="bold", size = 22),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 18, angle = 0), 
        axis.text.y = element_text(size = 14, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))


library(see)

tdata_sub <- tdata_1814

## first, turn sID into a factor
tdata_sub$sID <- factor(tdata_sub$sID)

pd <- position_dodge(width = 0.3)

tdata_sub$valueJitter <- jitter(tdata_sub$value, factor = 1, amount = 0.04)

theme_set(theme_light(base_size = 20, base_family = "Poppins"))

# new labes for the facets 
#process.labs <- c("Process: Generative", "Process: Preventive")
#names(process.labs) <- c("generative", "preventive")

#valence.labs <- c("Effect valence: Positive", "Effect Valence: Negative")
#names(valence.labs) <- c("positive", "negative")


g <- ggplot(tdata_sub, aes(x=variable2, y=value, color = Links, fill = Links)) +
  guides(fill=FALSE)+
  #facet_grid(Valence ~ Process, labeller = labeller(Process = process.labs, Valence = valence.labs))+
  #ggtitle("Subjects' causal srength ratings") +
  scale_y_continuous(limits = c(-0.05, 1.05), breaks=seq(0, 1, 0.1), expand = c(0,0)) +
  #scale_x_discrete(labels=c("Downward chain", "Upward chain")) +
  #stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black", alpha =0.5) +
  stat_summary(aes(group = Links, fill = Links, color = Links), fun.data = mean_cl_boot, geom = "errorbar", width = 0, size = 1) +
  stat_summary(aes(group = Links, fill = Links, color = Links), fun.y=mean, geom="line", size = 1.5, linetype = "solid", alpha = 0.6)+
  stat_summary(aes(group = Links, fill = Links, color = Links), fun.y=mean, geom="point", shape = 22, size = 5, group=1, alpha = 0.8)+
  #stat_summary(fun.y=median, geom="point", color = "black", shape = 3, size = 4, group=1, alpha = 1, position = position_dodge(width = 0.5))+
  #labs(x = "Link of Chain", y = "Causal Strength Rating") +
  #scale_color_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  #scale_fill_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  theme(legend.position = "top")+
  myTheme
g


#ggsave("results_lines8.svg",width=7,height=6)
#ggsave("results_lines8.pdf",width=7,height=6)
```

Indeed, the longer chain seems to lead to more dilution (but the effect is very weak). 


ANOVA: 

```{r}
a1 <- aov_car(value ~ Links + variable2 + Error(sID/(Links+variable2)), tdata_sub)
a1

```
Not signifiant.


Directed Contrast for this interaction:

```{r}
############### 
# a conditional analysis 

ls2 <- lsmeans(a1, c("Links","variable2")) # group means by between-condition
ls2

# simple main effects 
pairs(pairs(ls2),adjust = "none") # compares rep-measure differences separately for each between-factor level

```
Row "(four first - four last) - (eight first - eight last)" shows the relevant interaction contrast. This is not significant.

