---
title: "No perceived dilution of causal strength in binary chains"
author: "Simon Stephan"
output: html_document
---

```{r setup, include=FALSE}
# packages
library(ez)
library(reshape2)
library(reshape)
library(ggplot2)
library(plyr)
library(pastecs)
library(ez)
library(data.table)
library(tidyverse) 

library(showtext)


font_add_google("Poppins", "Poppins")
font_add_google("Roboto Mono", "Roboto Mono")
showtext_auto()
```


```{r}
# read in data
#tdata.wide <- read.delim("dummy_data.txt", header=TRUE, sep="\t", na.strings="NA", dec=".", strip.white=TRUE)
tdata <- read.delim("data_Exp4.txt", header=TRUE, sep="\t", na.strings="NA", dec=".", strip.white=TRUE)
```


# Demographics

```{r}
# demographics 

tdata_age <- tdata 

min(tdata_age$Age)
max(tdata_age$Age)
mean(tdata_age$Age)
sd(tdata_age$Age)

# 1 = male, 2 = female, 3 = other
table(tdata$Sex)
```
1 = male, 2 = female, 3 = non-binary, 4 = don't want to say




```{r, echo = FALSE}
# reorder factor 

# to create chart, the data must be in long format and only contain the relevant dependent variables

# 1. make a subset with only the relevant dvs 

tdata_sub <- subset(tdata, select = 1:9)

dat_present <- subset(tdata_sub, select = c(1,3,5,7,9))
colnames(dat_present)<- c("sID", "first", "second", "third", "fourth")

dat_absent <- subset(tdata_sub, select = c(1,2,4,6,8))
colnames(dat_absent)<- c("sID", "first", "second", "third", "fourth")



# 2. reshape into long format 
tdata_links_p <- dat_present %>% gather(variable, value, 2:5)
tdata_links_p$Event <- "present"
tdata_links_p$value <- tdata_links_p$value * 0.01 # Recode DV so that values range from 0 to 1

tdata_links_p$variable <- factor(tdata_links_p$variable, levels = c("first", "second", "third", "fourth"), 
                          labels = c("1st", "2nd", "3rd", "4th"))

tdata_links_a <- dat_absent %>% gather(variable, value, 2:5)
tdata_links_a$Event <- "absent"
tdata_links_a$value <- tdata_links_a$value * 0.01 # Recode DV so that values range from 0 to 1


tdata_links_a$variable <- factor(tdata_links_a$variable, levels = c("first", "second", "third", "fourth"), 
                          labels = c("1st", "2nd", "3rd", "4th"))


tdata_links <- rbind(tdata_links_a, tdata_links_p)



tdata_links$Event <- factor(tdata_links$Event, levels = c("present", "absent"), 
                          labels = c("present", "absent"))

tdata_links$value <- as.numeric(tdata_links$value)
```



# Graphs


```{r}
myTheme <- theme(plot.title = element_text(face="bold", size = 22),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 18, angle = 0), 
        axis.text.y = element_text(size = 14, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))


library(see)

tdata_sub <- tdata_links

## first, turn sID into a factor
tdata_sub$sID <- factor(tdata_sub$sID)

pd <- position_dodge(width = 0.3)

tdata_sub$valueJitter <- jitter(tdata_sub$value, factor = 1, amount = 0.04)

theme_set(theme_light(base_size = 20, base_family = "Poppins"))


g <- ggplot(tdata_sub, aes(x=variable, y=valueJitter, group = sID)) +
  guides(fill=FALSE)+
  facet_grid(~ Event)+
  #ggtitle("Subjects' causal srength ratings") +
  scale_y_continuous(limits = c(-0.05, 1.05), breaks=seq(0, 1, 0.1), expand = c(0,0)) +
  #scale_x_discrete(labels=c("Downward chain", "Upward chain")) +
  #stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black", alpha =0.5) +
  geom_violinhalf(aes(y = value, group = variable), color = NA, position=position_dodge(1), alpha = 0.2)+
  geom_line(position = pd, color = "red", size = 1, alpha=0.04) +
  geom_point(position = pd, alpha = 0.2, fill = "red", color = "red") +
  stat_summary(aes(y = value,group=1), fun.data = mean_cl_boot, geom = "errorbar", width = 0, size = 1) +
  stat_summary(aes(y = value,group=1), fun.y=mean, colour="red", geom="line",group=1, size = 1.5, linetype = "solid", alpha = 0.6)+
  stat_summary(aes(y = value,group=1), fun.y=mean, geom="point", color = "black", fill = "red", shape = 22, size = 5, group=1, alpha = 0.8)+
  stat_summary(aes(y = value,group=1), fun.y=median, geom="point", color = "black", shape = 3, size = 4, group=1, alpha = 1, position = position_dodge(width = 0.5))+
  labs(x = "Link of Chain", y = "Causal Strength Rating") +
  #scale_color_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  #scale_fill_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  theme(legend.position = "none")+
  myTheme
g


ggsave("results_lines.svg",width=7,height=6)
ggsave("results_lines.pdf",width=7,height=6)
```

```{r}
myTheme <- theme(plot.title = element_text(face="bold", size = 22),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 18, angle = 0), 
        axis.text.y = element_text(size = 14, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))


library(see)

tdata_sub <- tdata_links_p

## first, turn sID into a factor
tdata_sub$sID <- factor(tdata_sub$sID)

pd <- position_dodge(width = 0.3)

tdata_sub$valueJitter <- jitter(tdata_sub$value, factor = 1, amount = 0.04)

theme_set(theme_light(base_size = 20, base_family = "Poppins"))


g <- ggplot(tdata_sub, aes(x=variable, y=valueJitter, group = sID)) +
  guides(fill=FALSE)+
  #facet_grid(~ Event)+
  #ggtitle("Subjects' causal srength ratings") +
  scale_y_continuous(limits = c(-0.05, 1.05), breaks=seq(0, 1, 0.1), expand = c(0,0)) +
  #scale_x_discrete(labels=c("Downward chain", "Upward chain")) +
  #stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black", alpha =0.5) +
  geom_violinhalf(aes(y = value, group = variable), color = NA, position=position_dodge(1), alpha = 0.2)+
  geom_line(position = pd, color = "red", size = 1, alpha=0.04) +
  geom_point(position = pd, alpha = 0.2, fill = "red", color = "red") +
  stat_summary(aes(y = value,group=1), fun.data = mean_cl_boot, geom = "errorbar", width = 0, size = 1) +
  stat_summary(aes(y = value,group=1), fun.y=mean, colour="red", geom="line",group=1, size = 1.5, linetype = "solid", alpha = 0.6)+
  stat_summary(aes(y = value,group=1), fun.y=mean, geom="point", color = "black", fill = "red", shape = 22, size = 5, group=1, alpha = 0.8)+
  stat_summary(aes(y = value,group=1), fun.y=median, geom="point", color = "black", shape = 3, size = 4, group=1, alpha = 1, position = position_dodge(width = 0.5))+
  labs(x = "Link of Chain", y = "Causal Strength Rating") +
  #scale_color_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  #scale_fill_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  theme(legend.position = "none")+
  myTheme
g


ggsave("results_lines_p.svg",width=5,height=6)
ggsave("results_lines_p.pdf",width=5,height=6)
```

```{r}
myTheme <- theme(plot.title = element_text(face="bold", size = 22),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 18, angle = 0), 
        axis.text.y = element_text(size = 14, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))


library(see)

tdata_sub <- tdata_links_a

## first, turn sID into a factor
tdata_sub$sID <- factor(tdata_sub$sID)

pd <- position_dodge(width = 0.3)

tdata_sub$valueJitter <- jitter(tdata_sub$value, factor = 1, amount = 0.04)

theme_set(theme_light(base_size = 20, base_family = "Poppins"))


g <- ggplot(tdata_sub, aes(x=variable, y=valueJitter, group = sID)) +
  guides(fill=FALSE)+
  #facet_grid(~ Event)+
  #ggtitle("Subjects' causal srength ratings") +
  scale_y_continuous(limits = c(-0.05, 1.05), breaks=seq(0, 1, 0.1), expand = c(0,0)) +
  #scale_x_discrete(labels=c("Downward chain", "Upward chain")) +
  #stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black", alpha =0.5) +
  geom_violinhalf(aes(y = value, group = variable), color = NA, position=position_dodge(1), alpha = 0.2)+
  geom_line(position = pd, color = "red", size = 1, alpha=0.04) +
  geom_point(position = pd, alpha = 0.2, fill = "red", color = "red") +
  stat_summary(aes(y = value,group=1), fun.data = mean_cl_boot, geom = "errorbar", width = 0, size = 1) +
  stat_summary(aes(y = value,group=1), fun.y=mean, colour="red", geom="line",group=1, size = 1.5, linetype = "solid", alpha = 0.6)+
  stat_summary(aes(y = value,group=1), fun.y=mean, geom="point", color = "black", fill = "red", shape = 22, size = 5, group=1, alpha = 0.8)+
  stat_summary(aes(y = value,group=1), fun.y=median, geom="point", color = "black", shape = 3, size = 4, group=1, alpha = 1, position = position_dodge(width = 0.5))+
  labs(x = "Link of Chain", y = "Causal Strength Rating") +
  #scale_color_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  #scale_fill_manual(name = "Entity",values=c("#fc9272", "#3182bd"))+
  theme(legend.position = "none")+
  myTheme
g


ggsave("results_lines_a.svg",width=5,height=6)
ggsave("results_lines_a.pdf",width=5,height=6)
```




# Descriptive Stats


```{r, echo = FALSE, warning = FALSE, message = FALSE}

################################################################################################################
##################################### Statistical Analyses #####################################################
################################################################################################################
library(pastecs)
library(lme4)
library(nlme)
library(ez)


##################################### Create descriptive stats ###################################

by(tdata_links$value, list(tdata_links$variable, tdata_links$Event), stat.desc , basic = FALSE)


```



# Inferential Statistics


Repeated-Measures ANOVA 

```{r}
library(afex)
library(emmeans)

a1 <- aov_car(value ~ variable*Event + Error(sID/(variable*Event)), tdata_links)
a1

```

Main effect for Event, because ratings are higher if proximate cause is present. No effect vor "variable" (the link of the chain) and "Event" as predicted. Also no interaction, as predicted.


```{r}
# subset for the ratings for "present" 
tdata_sub <- tdata_links_p
tdata_sub <- subset(tdata_sub, Event == "present")
```



```{r}
# Polynomial Contrasts
#library(Rcmdr)
# Quantitative Trend analysis

contrasts(tdata_sub$variable) <- "contr.poly" # define contrast coefficients

Trend <- aov(value ~ variable, data=tdata_sub)
summary.lm(Trend)

```

No significant trend, as predicted.

```{r}
# contrast 1st vs. 4th link 

tdata_14 <- subset(tdata_sub, variable == "1st" | variable == "4th")
tdata_sub <- tdata_14

a1 <- aov_car(value ~ variable + Error(sID/(variable)), tdata_sub)

# contrast

ls2 <- lsmeans(a1, c("variable")) # group means by between-condition
ls2

# simple main effects 
t <- pairs(ls2) # compares rep-measure differences separately for each between-factor level
t

```

Yes, the contrast is significant (see "contrast" output). 




Compute a 95 CI for the difference:


```{r}
confint(t, adjust = "none")
```
Almost no net difference, as predicted.


Visualize: 

```{r}

effect <- "Mdiff"
Mdiff <- -0.000993  # the estimated difference from the output above
half_CI <- (0.019 - -0.021)*0.5
CI_low <- Mdiff - half_CI
CI_up <- Mdiff + half_CI

Mdiff
CI_low
CI_up



# Plot 

myTheme <- theme(plot.title = element_text(face="bold", size = 22),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 18, angle = 0), 
        axis.text.y = element_text(size = 25, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        #panel.grid.minor = element_blank(), 
        #panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))

theme_set(theme_light(base_size = 30, base_family = "Poppins"))



barchart <- ggplot()+
  myTheme+
  #guides(fill=FALSE)+
  #facet_wrap(~Latency + SampleSize, ncol=2)+
  #ggtitle("Mean difference (95% CI)") +
  #coord_cartesian(ylim=c(-0.1,2)) + 
  scale_y_continuous(limits = c(-0.1, 0.5), breaks=seq(-0.1, 0.5, 0.1), expand = c(0,0)) +
  scale_x_discrete(labels=c("r")) +
  #annotate("rect", xmin=1.7, xmax=2.3, ymin=0.95, ymax=1.05, color="#31a354", fill = "white", size = 1) +
  #stat_summary(fun.y=mean, colour="grey20", geom="point", shape = 21, size = 3)+
  #stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black")+
  #stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.90), width = 0.2) +
  #geom_jitter(width = 0.3, height = 0.02, alpha = 0.6, colour = "red") +
  #ggtitle("Means (95% bootstr. CIs)") +
  #theme(axis.text.x = element_text(size = 10, angle = 0, hjust = 0.5))+
  labs(x= "", y = "1st - 4th Link") +
  #scale_color_manual(values=c("#005083",  "#f0b64d"))# +
  #scale_fill_manual(values=c("#969696",  "#969696"))
  #annotate("point", x = 1, y = 100, colour = "firebrick", size = 2)+
  #annotate(xmin = -Inf, xmax = Inf, ymin = 4.77-1.96*0.297, ymax = 4.77+1.96*0.297, geom = "rect", alpha = 0.2, fill = "firebrick")+
  #annotate(xmin = -Inf, xmax = Inf, ymin = 5.02-1.96*0.372, ymax = 5.02+1.96*0.372, geom = "rect", alpha = 0.2, fill = "blue")+
  #annotate(geom = "hline",yintercept = 100, y = 100, color = "red")+
  annotate("pointrange", x = 1, y = Mdiff, ymin = CI_low, ymax = CI_up, colour = "black", size = 1.5, shape = 24, fill = "darkgrey")+
  #annotate("pointrange", x = 2, y = 5.02, ymin = 5.02-1.96*0.372, ymax = 5.02+1.96*0.372, colour = "blue", size = 0.8, shape = 15)+
  #annotate("text", x = 0.5, y = 2.6, family = "Poppins", size = 6, color = "gray20", label = "Impfeffekt")+
  #geom_curve(aes(x = 0.5, y = 3, xend = 0.9, yend = 4),arrow = arrow(length = unit(0.03, "npc")),color = "gray20", curvature = +0.2)+
  #annotate("text", x = 1.8, y = 2.6, family = "Poppins", size = 6, color = "gray20", label = "Dosierungseffekt")+
  #geom_curve(aes(x = 1.8, y = 3, xend = 2, yend = 4),arrow = arrow(length = unit(0.03, "npc")),color = "gray20", curvature = +0.2)+
  annotate(geom = "hline",yintercept = 0, y = 0, color = "red", size = 1.2)+
  theme(plot.background = element_rect(
    fill = "white",
    colour = "black",
    size = 1
  ),
    axis.title.y = element_text(size = 30))


barchart

#ggsave("delta_1st_vs_6th.svg",width=2.5,height=4)
ggsave("delta_1st_vs_4th.pdf",width=2.5,height=4)



```


What Cohen's d does this difference correspond to? 










```{r}
# since we have a repeated-meausres design, we now need the correlations of the ratings
library(dplyr) # for pipe operator
dat_wide <- spread(tdata_14, variable, value)
colnames(dat_wide) <- c("sID", "Links", "first", "last")
dat_wide -> t
r <- cor(t$first, t$last)
r
```


```{r}
# now compute ES and SE and CI of it
# using the esc package because it gives SE of the ES directly
library(esc)
dat <- tdata_14
# get means and sds
m1 <- dat %>%
          filter(variable == "1st")%>%
          summarize(Mean1 = mean(value))

sd1 <- dat %>%
          filter(variable == "1st")%>%
          summarize(SD1 = sd(value))


m2 <- dat %>%
          filter(variable == "4th")%>%
          summarize(Mean2 = mean(value))

sd2 <- dat %>%
          filter(variable == "4th")%>%
          summarize(SD2 = sd(value))



esc_mean_sd(
  grp1m = m1[,1], grp1sd = sd1[,1], grp1n = length(dat$sID)/2,
  grp2m = m2[,1], grp2sd = sd2[,1], grp2n = length(dat$sID)/2,
  r = r,
  es.type = "d"
)
```

